### 2017-04-01 paper/evaluation.tex
pass on dimension
dimensions and rqs

We pose the following research questions, organized by the dimensions
presented in Section~\ref{sec:intro}.

\newcommand{\numRQA}{RQ1}
\newcommand{\numRQB}{RQ2}
\newcommand{\numRQC}{RQ3}
\newcommand{\numRQD}{RQ4}
\newcommand{\numRQE}{RQ5}
\newcommand{\numRQF}{RQ6}

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
  test suites\Comment{ in open-source projects}?}
\newcommand{\RQB}{How time is distributed across test cases?}
\newcommand{\RQC}{How prevalent is the use of test suite
  parallelization\Comment{ in open-source projects}?}
\newcommand{\RQD}{What are the speedups obtained with parallelization
  (in projects that actually use it) on cost?}
\newcommand{\RQE}{What are the main reasons that prevent developers
  from using test suite parallelization?}
\newcommand{\RQF}{How different configurations of parallel execution affect testing
  cost and flakiness?}

\begin{itemize}
\item Potential
  \begin{itemize}
  \item \textbf{\numRQA.} \RQA
  \item \textbf{\numRQB.} \RQB    
  \end{itemize}    
\item Usage
  \begin{itemize}
  \item \textbf{\numRQC.} \RQC    
  \end{itemize}
\item Effectiveness
  \begin{itemize}
  \item \textbf{\numRQD.} \RQD
  \end{itemize}
\item Perception
  \begin{itemize}
  \item \textbf{\numRQE.} \RQE
  \end{itemize}
\item Tradeoffs
  \begin{itemize}
  \item \textbf{\numRQF.} \RQF    
  \end{itemize}          
\end{itemize}

>>>>

We pose the following research questions, organized by the dimensions
of analysis we presented in Section~\ref{sec:intro}.

\newcommand{\numRQA}{RQ1}
\newcommand{\numRQB}{RQ2}
\newcommand{\numRQD}{RQ3}
\newcommand{\numRQC}{RQ4}
\newcommand{\numRQE}{RQ5}
\newcommand{\numRQF}{RQ6}

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
  test suites\Comment{ in open-source projects}?}
\newcommand{\RQB}{How time is distributed across test cases?}
\newcommand{\RQC}{How prevalent is the use of test suite
  parallelization\Comment{ in open-source projects}?}
\newcommand{\RQD}{What are the speedups obtained with parallelization
  (in projects that actually use it) on cost?}
\newcommand{\RQE}{What are the main reasons that prevent developers
  from using test suite parallelization?}
\newcommand{\RQF}{To which extent parallel execution configurations affect testing
  cost and flakiness?}

\begin{itemize}
\item Potential
  \begin{itemize}
  \item \textbf{\numRQA.} \RQA
  \item \textbf{\numRQB.} \RQB    
  \end{itemize}
\item Effectiveness
  \begin{itemize}
  \item \textbf{\numRQD.} \RQD
  \end{itemize}  
\item Adoption
  \begin{itemize}
  \item \textbf{\numRQC.} \RQC    
  \item \textbf{\numRQE.} \RQE
  \end{itemize}
\item Tradeoff
  \begin{itemize}
  \item \textbf{\numRQF.} \RQF    
  \end{itemize}          
\end{itemize}
